Rclean: A Tool for Writing Cleaner, More Transparent Code

### 2020-02-13 joss/paper.rmd
Manual brackets and yaml

The growth of programming in the sciences has been explosive in the
last decade. This has facilitated the rapid advancement of science
through the agile development of computational tools. However,
concerns have begun to surface about the reproducibility of scientific
research in general [@Peng2011, @Baker2016] and the potential issues
stemming from issues with analytical software [@Pasquier2017,
@Stodden2018]. Specifically, there is a growing recognition across
disciplines that simply making data and software "available" is not
enough and that there is a need to improve the transparency and
stability of scientific software [@Pasquier2018].

>>>>

The growth of programming in the sciences has been explosive in the
last decade. This has facilitated the rapid advancement of science
through the agile development of computational tools. However,
concerns have begun to surface about the reproducibility of scientific
research in general [@Baker2016] and the potential issues stemming from
issues with analytical software [@Stodden2018]. Specifically, there is a
growing recognition across disciplines that simply making data and
software "available" is not enough and that there is a need to improve
the transparency and stability of scientific software [@Pasquier2018].
